Contextual Identity: A Framework for Usable Privacy

### 2013-02-26 paper.tex
switch to ieee
replace authors
minor changes, mostly stubs

%\documentclass[11pt,letterpaper,onecolumn]{article}
\documentclass{llncs}
\usepackage{llncsdoc}
%\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}

\usepackage{epsfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{ltxtable}
\usepackage{tabularx}
\usepackage{hhline}
\usepackage{color,colortbl}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{comment}
\usepackage{fullpage}

@@

%\author{Monica Chew,Sid Stamm\\
%\email{\{mmc,sid\}@mozilla.com}}
%\institute{Mozilla}
\maketitle
\section{Introduction}
\begin{quote}I am large, I contain multitudes. --- Walt Whitman,
\begin{em}Song of Myself\end{em} \end{quote}

@@

We provide a simple formalization of the notion of contextual identity, use it
as a framework to understand existing privacy violations, and analyze
mitigations for those violations.

@@

@@

Barth et al.~provide a formal model for contextual integrity of user
data~\cite{barth}. The contextual integrity model focuses on the flow of
personal information in terms of knowledge states held by agents rather than on
user identity, and works well for modeling privacy legislation and policy. In
contrast, this work's model provides a simple framework to understand users'
ability to represent which contextual identity they want to project, and works
well for modeling how software features affect users' ability to assert choice
and control.

@@

@@

\bibliographystyle{plain}
\bibliography{paper}
\end{document}

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}

\usepackage{epsfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{ltxtable}
\usepackage{tabularx}
\usepackage{hhline}
\usepackage{color,colortbl}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{comment}
%\usepackage{fullpage}

@@

\author{Monica Chew,Sid Stamm\\
\tt{\{mmc,sid\}@mozilla.com}}
%\institute{Mozilla}
\maketitle
\section{Introduction}
\begin{quote}I am large, I contain multitudes. --- Walt Whitman,
\begin{em}Song of Myself\end{em} \end{quote}

@@

@@

Barth et al.~provide a formal model for contextual integrity of user
data~\cite{barth}. The contextual integrity model focuses on the flow of
personal information in terms of knowledge states held by agents rather than on
user identity, and works well for modeling privacy legislation and policy. Two
drawbacks of this work are that it is incapable of modeling information that is
about more than one person, and it is the type of information rather than the
content of the information that determines whether or not integrity is
violated. In the context of social networks, information is rarely ever about a
single person, and the tone of the message is as important to user
happiness as the content of the message.

@@

@@

\section{How do users think about identity?}
\subsection{Blushproof}
\subsection{Cookie statistics}

@@

%Convert to IEEE?
\bibliographystyle{plain}
\bibliography{paper}
\end{document}
